A Topography of Climate Change Research

### 2017-11-29 pres/Forster_29_11_09.tex
pres done

\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{pgfgantt}

@@

\begin{frame}{Research Questions}
\begin{itemize}
	\item What topics are discovered endogenously from a corpus of > 200,000 abstracts on climate change?
	\item How do these topics describe the structure of the literature?
	\item Which topics have grown recently?
	\item Which topics are better and less well represented in IPCC assessment reports?
\end{itemize}

@@

@@

@@

@@

@@

\begin{itemize}
	\item Endogenously discovered topics make substantive sense of an unmanageable dataset of climate-relevant literature
	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
	\item Topics from the same IPCC working group are more likely to be connected to each other.
	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
\end{itemize}

>>>>

\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{tikz}
\usepackage{pgfgantt}
\usepackage{booktabs}

@@

\begin{frame}{Research Questions}
\begin{itemize}
	\item What topics are discovered endogenously from a corpus of > 200,000 abstracts on climate change?
	\item How do these topics describe the structure of the literature?
	\item Which topics have grown recently?
	\item Which topics are better and less well represented in IPCC assessment reports?
\end{itemize}
\end{frame}

@@

\begin{frame}{Preliminary results - Map}

\begin{figure}
			\includegraphics[width=\linewidth]{../plots/pca_map.png}
			\caption{Topic Map, with topics placed according to Principal Component Analysis of topic-term matrix}
\end{figure}

@@

\begin{frame}{Preliminary results - structure - Sustainability}

@@

\begin{frame}{Preliminary results - structure - Sustainability}

\begin{columns}
	\begin{column}{0.6\linewidth}
		\begin{center}			
			\includegraphics[width=\linewidth]{../plots/health_sustain_386.PNG}
		\end{center}
	\end{column}
	\begin{column}{0.4\linewidth}
		\begin{center}
			\begin{itemize}
				\item The flatness of its distribution across documents indicates a topic that occurs
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}

%% Sus table

\begin{frame}{Preliminary results - structure - Sustainability}
\begin{table}
	\footnotesize
	\renewcommand{\arraystretch}{2}
\begin{tabular}{p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}}
	\toprule 
	{polici, govern, tax} & {adapt, vulner, strategi}  & {urban, citi, area} \\ 
	\midrule 
	How Research-Prioritization Exercises Affect Conservation Policy & Methodological choices in solution-oriented adaptation research: a diagnostic framework & A review of urban ecosystem services: six key challenges for future research  \\ 
	Role of hydrology and economics in water management policy under increasing uncertainty & When not every response to climate change is a good one: Identifying principles for sustainable adaptation & Lines of Tradition and Recent Approaches to Urban Ecology, Focussing on Germany and the USA \\ 
	Informing food policy: balancing the evidence & Informed adaptation: Ethical considerations for adaptation researchers and decision-makers & Advancing understanding of the complex nature of urban systems \\ 
	The identification of priority policy options for UK nature conservation & Future oriented conservation: knowledge governance, uncertainty and learning & Sustainable urban landscapes: South African perspectives on transdisciplinary possibilities \\ 
	Environmental education policy research challenges and ways research might cope with them & Towards an integrated agenda for adaptation research: theory, practice and policy & A conceptual framework for addressing complexity and unfolding transition dynamics when developing sustainable adaptation strategies in urban water management \\
	\bottomrule
\end{tabular}

\end{table}

@@

			\includegraphics[width=0.8\linewidth]{../plots/ipcc_topics_wg_386.png}

\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}

\begin{table}

	\input{../tables/386_wg_1_2}

\end{table}

%%%%%%%%

\begin{frame}{Preliminary results - Inter-working Group topics - WG 1 and 3}

\begin{table}

\input{../tables/386_wg_1_3}

\end{table}

%%%%%%%

\begin{frame}{Preliminary results - Inter-working Group topics - WG 2 and 3}

\begin{table}

\input{../tables/386_wg_2_3}

\end{table}

@@

\begin{itemize}
	\item Endogenously discovered topics make substantive sense of an unmanageable dataset of climate-relevant literature
	\item Topic modelling discovers over-arching topics such as that on sustainability and research priorities, as well as individual, fast growing topics such as biochar or CCS
	\item Matching documents to IPCC references, we can describe topics that belong to or bridge IPCC working groups
	\item Quantitative evidence is found to support policy makers' dissatisfaction with a lack of `solution orientation' in IPCC reports \citep{Kowarsch2017} 
\end{itemize}
